Comparison of Confidence Interval in the OLS and Ridge Linear Regression Model: A Comparative study via Simulation

### 2024-08-29 draft_1.qmd
continued

---
title: "Comparison of Confidence Interval in the OLS and Ridge Linear Regression Model: A Comparative study via Simulation"
format: #docx
    tandf-pdf:
      keep-tex: true  
    tandf-html: default
author:
  - name: Sultana Mubarika Rahman Chowdhury
    affiliations:
      - ref: biostat
    orcid: 
    email: schow034@fiu.edu
  - name: B.M Golam Kibria
    affiliations:
      - ref: stat
  - name: Zoran Bursac
    affiliations:
      - ref: biostat
affiliations:
  - id: biostat
    name: Florida International University
    department: Biosatistics Department
    address: 11200 SW 8th St
    city: Miami, Fl
    country: USA
    postal-code: 33199
  - id: stat
    name: Florida International University
    department: Department of Mathematics and Statistics
    address: 11200 SW 8th St 
    city: Miami, Fl
    country: USA
    postal-code: 33199
abstract: |
  Write down the abstract here
keywords: 
  - Multiple Linear Regression
  - Ridge Regression
  - Multicolinearity
bibliography: bibliography.bib  
---

@@

One of the key assumption of the widely used multiple linear regression model is that the predictors need to be independent of each other. Violating the assumption of independence 
results in an issue known as multicollinearity. Multicollinearity occurs when two or more independent variables are highly correlated with each other. It causes standard error of the OLS coefficient to increase resulting in wide confidence intervals and less reliable results. Identifying and interpreting significant predictors also becomes difficult. As the field of study progressed, researchers developed a number of methods to address presence of multicollinearity in data. Ridge regression [@hoerl1970ridge], Lasso,

>>>>

---
title: "Comparison of Confidence Interval in the OLS and Ridge Linear Regression Model: A Comparative study via Simulation"
format: #docx
    tandf-pdf:
      keep-tex: true  
    tandf-html: default
author:
  - name: Sultana Mubarika Rahman Chowdhury
    affiliations:
      - ref: biostat
    orcid: 
    email: schow034@fiu.edu
  - name: B.M. Golam Kibria
    affiliations:
      - ref: stat
  - name: Zoran Bursac
    affiliations:
      - ref: biostat
affiliations:
  - id: biostat
    name: Florida International University
    department: Biosatistics Department
    address: 11200 SW 8th St
    city: Miami, Fl
    country: USA
    postal-code: 33199
  - id: stat
    name: Florida International University
    department: Department of Mathematics and Statistics
    address: 11200 SW 8th St 
    city: Miami, Fl
    country: USA
    postal-code: 33199
abstract: |
  Write down the abstract here
keywords: 
  - Multiple Linear Regression
  - Ridge Regression
  - Multicolinearity
bibliography: bibliography.bib  
---

@@

One of the key assumption of the widely used multiple linear regression model is that the predictors need to be independent of each other. Violating the assumption of independence results in an issue known as multicollinearity. Multicollinearity, originally identified by @frisch1934statistical, is the state in which two or more independent variables show a strong correlation with one another. It causes standard error of the OLS estimator to increase resulting in wide confidence intervals and less reliable results. Identifying and interpreting significant predictors also becomes difficult [@saleh2019theory]. Increasing the sample size, eliminating the highly correlated variables, Principal component analysis are some of the ways to avoid multicollinearity but with the risk of losing either valuable information or interpretability.

As the field of study progressed, researchers developed a number of methods to perform better than OLS in presence of multicollinearity in data by introducing bias to the estimator to gain smaller variance. Ridge regression [@hoerl1970ridge], Lasso [@tibshirani1996regression], Stein estimator [@stein1956inadmissibility], Modified ridge regression, Liu estimator [@liu1993new], 
Kibria-Lukman estimator [@kibria2020new] are some them.
